
\subsubsection{Code Reviews}
\label{sec:code-reviews}

The SW components have been subjected to code reviews to detect design
errors prior to testing, and to complement testing. An example of the
code reviews is presented in the ensuing section. 


\subsubsection{Code Review of the SCADE Package trainData}
\label{sec:VnV-SCADETrainData-DLR}

\paragraph{Contributing project partners}
This work has been performed by the DLR.

\paragraph{Process step}
This activity is part of the verification of the SW components. It
contributes to the SW Component Verification Report (5-26). 

\paragraph{Object of verification}
The SCADE package \texttt{trainData} incorporating the sub packages \texttt{trainData\_
pkg} and \texttt{trainData\_Types\_pkg}.

\paragraph{Available specification}
The package was checked against the ADD document (D3.5.4) and the ETCS
specification Subset-026, \cite[Sec.~3.18.3]{subset-026:3.3.0}.

\paragraph{Objective}
The objective is to establish plausibility that the SCADE package
conforms to the specification.

\paragraph{Method/Approach}
The verification has been performed by comparing implementation given
by the SCADE model with the corresponding specifications of Subset~026
and the ADD document.

\paragraph{Means/Tools}
The verification has been performed using the editing capabilities of
the SCADE Suite to display the model, and to search and navigate.

\paragraph{Results}
The review uncovered some incomplete coverage of the requirements due
to the absence of some implementation packages. The ramifications need
to be analyzed. 

% \paragraph{Observations/Comments}
% % An optional section where anything can be included which has been
% % observed without direct connection

% \paragraph{Conclusion}
% %What has been achieved, what is missing, what has been learned
