\subsection{The Function \poke}

The function \poke converts an integer to a bit sequence and writes it
into a bit stream.
Its function signature reads as follows:
\begin{lstlisting}[style = acsl-block]
int      Bitwalker_Poke(unsigned int Startposition,
                        unsigned int Length,
                        uint8_t Bitstream[],
                        unsigned int BitstreamSizeInBytes,
                        uint64_t Value);
\end{lstlisting}


\subsubsection*{Arguments}

\begin{itemize}
    \item \texttt{Startposition} is the bit index in the bit stream 
    where the bit sequence starts.
    \item \texttt{Length} is the length of the bit sequence.
    \item \texttt{Bitstream} is the array which provides the bit stream.
    \item \texttt{BitstreamSizeInBytes} is the length of the array 
    containing the bit stream. 
    \item \texttt{Value} is the integer which shall be converted into a bit sequence.
\end{itemize}


\subsubsection*{Preconditions}

The following preconditions shall hold for the function arguments:

\begin{itemize}
\item \texttt{Bitstream} is a valid array of length \verb"BitstreamSizeInBytes"

\item \texttt{Startposition + Length} $\leq$ \verb"UINT_MAX".
\end{itemize}

Note that additional constraints are implicitly expressed by the use
of \emph{unsigned} integer types.


\subsubsection*{Description}

The function \poke converts a 64-bit unsigned integer to a bit sequence and 
writes it into a bit stream.

For $0 \leq x$ exists a shortest sequence of~0 and~1
$(b_0, b_1,\ldots,b_{n - 1})$
such that
\begin{align}
    \sum_{i=0}^{n-1} b_i \cdot 2^{(n - 1) - i} = x.
\end{align}

The function \poke tries to store the sequence $(b_0, b_1,\ldots,b_{n - 1})$
in the bit sequence of \texttt{Length} bits that starts
at bit index \texttt{Startposition}.

The return value of \poke depends on the following three cases:

\begin{itemize}
\item 
If the bit sequence is valid, then there are two cases:

\begin{itemize}
\item
If $\texttt{Length} \geq n$, then  the sequence
$(\overbrace{0,\ldots,0}^{\texttt{Length}-n},b_0, b_1,\ldots,b_{n - 1})$
is stored in the bit stream starting at \texttt{Startposition}.
The return value of \poke is 0.

\item
If $\texttt{Length} < n$, then the
sequence $(b_0, b_1,\ldots,b_{n - 1})$ cannot be stored and\\
\poke returns~$-1$.
\end{itemize}

\item 
If the bit sequence is not valid, then \poke returns~$-2$.
\end{itemize}

