\subsection{Identity of Verification Object}

The component \texttt{Train Positioning} provides the central functionality to determine the train position based on detected balises and their measured and announced distances. 

The component is defined in the \texttt{openETCS System Architecture and Design Specification} \cite{openETCS-Arch-I1} as F.2.2 Calculate Train Position. Here it is defined that the function shall cover the 
requirements defined in the SRS \cite{SRS} Chapter 3.6. 


Concepts for \texttt{Train Positioning} have been defined in two parallel work streams, which developed independently two documents and simulations to clarify their approach. To achieve one implementation in context of the overall openETCS architecture both concepts have to be integrated.
Respectively, this verification report is concerned with the following two groups of documents, which are handled as one verification object. All artifacts for verification and verification activities are documented in the github issue \url{https://github.com/openETCS/validation/issues/227}. 

\paragraph{\texttt{Train Positioning} concept 1}
\nl

\begin{tabular}{|l|p{8cm}|}
\hline \rule[-2ex]{0pt}{5.5ex} reviewed document & Train Position and Locations (concept document) \\ 
\hline \rule[-2ex]{0pt}{5.5ex}  & Train Position and Location Tester (Lab View Simulation) \\ 
\hline \rule[-2ex]{0pt}{5.5ex} github location & \url{https://github.com/openETCS/SRS-Analysis/commit/edc8a3238e59ad4d2a2440f39e4c791cf6bbf7bd} \\
\hline \rule[-2ex]{0pt}{5.5ex} comitted & 10. July 2014 \\ 
\hline \rule[-2ex]{0pt}{5.5ex} designer & Jan Welvaarts (concept)\\ 
\hline \rule[-2ex]{0pt}{5.5ex}  & Vincent Nuhaan (simulation)\\ 
\hline \rule[-2ex]{0pt}{5.5ex} covered specification &  SUBSET-26(SRS) chapter 3.6 version 3.3.0\\ 
\hline 
\end{tabular} 

\paragraph{\texttt{Train Positioning} concept 2}
\nl

\begin{tabular}{|l|p{8cm}|}
\hline \rule[-2ex]{0pt}{5.5ex} reviewed document &  openETCS Determine Train Location Procedure (concept document)\\ 
\hline \rule[-2ex]{0pt}{5.5ex} github location & \url{https://github.com/openETCS/SRS-Analysis/commit/153e793955b38c986dad3bfd8d3fbfe8d5ced77e} \\
\hline \rule[-2ex]{0pt}{5.5ex} comitted & 21. January 2014 \\ 
\hline \rule[-2ex]{0pt}{5.5ex} reviewed document & CalculateTrainPosition (SCADE report) \\ 
\hline \rule[-2ex]{0pt}{5.5ex} github location & \url{https://github.com/openETCS/modeling/commit/5cea2abbf67da49b324aa8307129b5c47aba2188#diff-9fd0c16adf976a82850cd9184a13f0f5} \\
\hline \rule[-2ex]{0pt}{5.5ex} comitted & 1. September 2014 \\
\hline \rule[-2ex]{0pt}{5.5ex} reviewed document & openETCS CalculateTrainPosition implementation Test Scenario 3\_linked\_2\_unlinkedBG (Test Scenarios) \\ 
\hline \rule[-2ex]{0pt}{5.5ex} github location & \url{https://github.com/openETCS/modeling/commit/3934d76f1fcba7cb28da7e8131f201182cc7d220} \\
\hline \rule[-2ex]{0pt}{5.5ex} comitted & 22. October 2014 \\
\hline \rule[-2ex]{0pt}{5.5ex} designer & Uwe Steinke (concept, SCADE implementation, Test Scenarios)\\ 
\hline \rule[-2ex]{0pt}{5.5ex} covered specification &  SUBSET-26(SRS) chapter 3.6 version 3.3.0\\ 
\hline 
\end{tabular} 

This verification reports only address the documents in the committed versions named above.

The verification mainly concentrated on the concept papers and took the simulation and the SCADE model only in consideration to specify the approach presented in the concept documents.

\subsection{Configuration related Components}

The functionality \texttt{Train Positioning} has been defined with respect to the SUBSET-26(SRS) chapter 3.6 version 3.3.0. 

The component limits have to be defined by the \texttt{openETCS System Architecture and Design Specification}, which has to present the interfaces either with respect to data from balise (and radio) messages defined in the SUBSET-26(SRS) chapters 7 and 8 or as in consistence with inputs and outputs of related functions. 

As the \texttt{openETCS System Architecture and Design Specification} have not been available at the beginning of the verification and not all functions interacting with \texttt{Train Positioning} are covered completely, the verification results have to accept assumptions made by the designers. Additionally, no further requirements for the interfaces have been assessed.