\section{Proof of : Shunting Initiated By Driver On}
\subsection{Files used for the proof}
\begin{tabular}{|c|c|}
\hline
Used node & Property file \\ \hline
Procedures::SH\_Initiated\_By\_Driver\_On & shunting\_initiated\_by\_driver\_on.hll \\
\hline
\end{tabular}

\subsection{What is proved ?}
We want to prove that the procedure SH\_Initiated\_By\_Driver\_On is a
correct implementation of the section 5.6 Shunting Initiated By Driver
(cf. D1).

This procedure is part of several scade sub-models as the procedure
Procedure\_StartOfMission or SH\_Initiated\_By\_Driver.

To prove this, a modelisation of the flowchart is proposed in the
property file. However, the flowchart is not entirely modelised
because the Scade model does not seem to represent all of
it. Requirements that are not modelised are the following :
\texttt{D030}, \texttt{A030}, \texttt{A095}, \texttt{S100} and
\texttt{A115}.

Moreover, the \texttt{S0} state of this flowchart is not modelised.
In fact, this state appears to be a condition that must be fulfilled
to start the reading of the flowchart. If at any state this condition
is no more true, then the reading of the flow chart stop and is
reinitialized.

\paragraph{Constraints used}
One constraint is used in this model. Without this constraint, a
counter-example is reachable.

This constraint specifies that the flowchart shall return to his
initial state a cycle after the dead-end state \texttt{A100} is
reached.

Actually, if this constraint is not verified, the Scade model could
return \texttt{False} for the request of ``End of Mission'' procedure
which contradicts the flowchart (\texttt{D040} and \texttt{A100} requirements).

In our implementation of the flowchart, this constraint is modelised
by verifying that when we are in \texttt{A100} the request of ``End of
Mission'' procedure correspond to the value of the input
\texttt{On-going Mission} as it is modelised in the Scade model.

This modelisation is justified by the fact that, according to
\texttt{A050}, \texttt{D040} and \texttt{A100}, if the input
\texttt{On-going Mission} is \texttt{True} then the ``End of Mission''
request is \texttt{True}, so equal to \texttt{On-going Mission}. Also,
as transition to SH mode is enable (\texttt{A050}) when ``End of
Mission'' request is made, the system should go to SH mode (or another
mode except SB mode). So the next cycle the driver should not execute
the shunting selection procedure and the next time this pocedure is
executed it should start a the initial state.


\subsection{Results}
Considering the constraint and our model, the Scade model of
SH\_Initiated\_By\_Driver\_On corresponds to the specification.


%\subsection{Conclusion and questions}
%\begin{itemize}
%\item The constraint used must be verified in an upper scade node.
%\item Parts of the flowcharts that are not modelised must be modelised
%  in another part of the scade model.
%\item Some output values should be precised in specifications when
%  reaching a state which sends some informations.
%\end{itemize}
