\documentclass{template/openetcs_article}
% Use the option "nocc" if the document is not licensed under Creative Commons
%\documentclass[nocc]{template/openetcs_article} 
\usepackage{lipsum,url}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{fixme}
\usepackage{lscape} 
\usepackage{pgfgantt}
\usepackage{adjustbox}
\usepackage{datetime}



%user specified macros
\input{macros.tex}


\graphicspath{{./template/}{.}{./images/}}
\begin{document}
\frontmatter
\project{openETCS}

%Please do not change anything above this line
%============================
% The document metadata is defined below

%assign a report number here
\reportnum{OETCS/WP4/DescriptionOfWork}

%define your workpackage here
\wp{Work Package 4: ``Validation \& Verification Strategy''}

%set a title here
\title{openETCS Validation \& Verification Strategy Work Package}

%set a subtitle here
\subtitle{Description of Work}

%set the date of the report here
\date{May 2013}

%define a list of authors and their affiliation here

\author{Marc Behrens}

\affiliation{WP4 Leader}
 
\author{Hardi Hungar}

\affiliation{WP4.1 Task Leader (Idetntification of tools and profile usage)}

\author{Ana Cavalli}

\affiliation{WP4.2 Task Leader (\VV of the formal model )}
 
\author{Jens Gerlach}

\affiliation{WP4.3 Task Leader (\VV of the implementation \/ code)}

\author{Hansj\"{o}rg Manz, Jan Welte}

\affiliation{WP4.4 Task Leader (Verification of the tools and processes)}

\author{Cyril Cornu }

\affiliation{WP4.5 Task Leader (Internal Assessment)}
  
% define the coverart
\coverart[width=350pt]{chart}

%define the type of report
\reporttype{Description of work}



\begin{abstract}
%define an abstract here

  This work package will comprise the activities concerned with
  verification and validation within openETCS. This includes \vv of
  development artifacts, that is, showing that models and code
  produced correctly express or implement what they are supposed
  to. And also, methods and tools to perform such tasks will be
  evaluated with the goal of assembling a suitable method and tool
  chain to support a full development.

  The first output of this work package is a \vv strategy and
  plan. The plan identifies the \vv tasks to be done according to the
  openETCS life cycle (perhaps variants of the life cycle) chosen in
  WP~2. It proposes methods and means to perform the tasks and defines
  the orchestration of the single activities to a full \vv support of
  developing the EVC software.

  Both model and code of the EVC software are subjected to \vv as they
  are produced by WP~3, and the tools and methods proposed in the \vv
  plan as well as those newly developed or improved in WP~7 are
  applied and evaluated in the process. Findings from these steps are
  iteratively fed back to the respective work package.

  A dedicated activity studies the safety aspect of \vv. It takes into
  cosideration what the standards (mainly EN~50128 and EN~50129)
  mandate and defines how these requirements can be met by the
  combination of process, methods and tools.

  The results of the work package are summarized in a final report on
  \vv at the end of the project.

\end{abstract}

%=============================
%Do not change the next three lines
\maketitle
\tableofcontents
\listoffiguresandtables
\newpage
%=============================

% The actual document starts below this line
%=============================


%Start here

\input{sections/introduction.tex}

\input{sections/tools_profile_usage.tex}

\input{sections/model_verification_validation.tex}

\input{sections/integration_code_verification_validation.tex}

\input{sections/tools_processes_verification.tex}

\input{sections/internal_assessment.tex}

\input{sections/gantt_chart.tex}

\nocite{*}
%===================================================
%Do NOT change anything below this line

\end{document}
