%\subsection{Formal Model Verification (TWT)}
%\label{sec:real-time-TA-openETCS}

This section describes TWT's plans regarding the formal verification
of the system model. While TWT's original approach has been focused
primarily on real-time aspects by employing timed automata and the
UPPAAL tool as described in Section~\ref{sct:twt:descrTA} (page
\pageref{sct:twt:descrTA}) our activities are now addressing formal
model verification on a broader scale.

TWT's work will be based on the following action items:
\begin{enumerate}
\item We will investigate the suitability of the open source toolkit
  CPN Tools\cite{CPNTools} for formal verfication (model checking) and
  simulation. The evaluation of CPN Tools will be aligned with the
  secondary toolchain assessment in WP7. A first step in the tool
  evaluation is the construction of an example model (currently
  ``Start of Mission'') from the ETCS specification.
  \item We will analyze whether/how UML/SysML statecharts and possibly
activity diagrams can be transformed to colored Petri nets to permit
their simulation and the formal verification of requirements.
  \item We will analyse the expressive power of the CPN Tools property
  language and whether the modeling formalism can replace UPPAAL for
  modelling and verifying timed aspects of ETCS components.
  \item We will provide feedback regarding ambiguities,
  inconsistencies and errors in the current ETCS standard based on our
  formalisation and the analysis of other models based on our
  approach.
  \item As the University of Braunschweig has experience with formal
  Petri net modelling, we will align our efforts with them.
  \item We will investigate, how our approach can be integrated in the
Eclipse environment and develop such integration if feasible with our
efforts.
  \item We plan to publish our results on action item 1.
\end{enumerate}

Please note that the above list may be subject to future change.
