%\subsection{Verification with Model-Based Simulation using SystemC (TWT, URO)}
%\label{sec:model-based-sim-openETCS}

In Section~\ref{sct:uro:systemc} (page \pageref{sct:uro:systemc}) the
basics of SystemC and the SysML/SystemC joint approach have been
described. TWT and the University of Rostock (URO) will work on this
concept based on the following action items:

\begin{enumerate}
  \item TWT will analyse methods for generating SystemC code from
  SysML models. In first investigations the Acceleo tool (Eclipse
  plugin, based on OMG standard) seems to be a promising candidate for
  model-to-text transformation.
  \item URO will build a modular and executable SystemC model for
  braking curves that is suitable for real-time simulation. An
  accompanying high-level SysML model will be constructed as well and
  will be means to test the transformation methods to be developed in
  the context of action item 1.
  \item TWT and URO plan to investigate which other parts of the ETCS
  specification can benefit from real-time simulation and build models
  accordingly.
  \item URO will investigate whether performance analysis based on the
  underlying hardware system is feasible within the openETCS
  project. This will allow to scale the hardware resources of the OBU
  system accordingly.
  \item In addition, using the results from action item 1, TWT and URO
    plan to transform existing SysML models (to be developed in WP3)
    to SystemC for real-time simulation.
  \item Evaluation (and possibly implementation) of an Eclipse
  integration
\end{enumerate}

Please note that the above list may be subject to future change.