% \chapter{Verification Plan for the Project openETCS}
% \label{sec:verification-plan-project}

\section{Verification Overview}
\label{sec:verif-overv}
Describe the organization, schedule, resources, responsibilities,
tools, techniques, and methodologies to be deployed in order to
perform the verification activities.


\subsection{Organisation}
Define the relationship of verification to other efforts such as
development, project management, quality assurance, and configuration
management. Define the lines of communication within the verification
effort, the authority for resolving issues, and the authority for
approving verification deliverables.

Organisation: a format for describing design artifacts subject to V\&V,
  and a feedback format for the findings during V\&V.

\subsection{Schedule}
The schedule summarizes the various verification tasks and their
relationship to the overall openETCS project.  It describes the
project life cycle and project milestones including completion dates.
Summarize the schedule of verification tasks and how verification
results provide feedback to the whole openETCS process to support
overall project management functions.  The objective of this section
is to define an orderly flow of material between project activities
and verification tasks.

According to the Description of Work of WP~4 \cite{WP4DoW}, the verification
activities will be structured into three main phases: 
\begin{enumerate}
\item First Level: Verification of prototypical system and API model
  and prototypical code,
\item Second Level: Verification of system model, functional API
  prototype model, code architecture and system API prototype
\item Third Level: Verification of final system and API model, final
  code and the functional API model
\end{enumerate}







\section{Verification Activities---User Stories}
\label{sec:verif-activ-user}

The term ``User Story'' as used in openETCS stands for any kind
application of tools, not just for the end user application of the
system (EVC software) which is to be developed. This section shall
describe such ``user stories'' of verifiers, i.e., it
shall describe where which method or tool is to going to be applied to
what artifact(s) (DAS2Vs). It thus shall tell coherently the
\textbf{story} of verification activities. Later (sub)sections provide
the organisational detail: \textbf{When} (Timeline,
Sec.~\ref{sec:verif-activ-timel}) and \textbf{Contribution} (which of
the verification obligations from Sec.~\ref{sec:verif-full-devel} are
tackled by what approach.

\bgcmmnt{the template for a user story should be included. It needs to
be updated: Verification Levels 1 and 2 should be covered. One may
include the old plan for Level 1, and mark changes appropriately.}


\subsection{Reviews and Inspections}
\label{sec:reviews-inspec-openETCS}

\input{WP41-V02-UserStory-ReviewsInspections.tex}

\subsection{Software Architecture Analysis Method (SAAM)}
\label{sec:saam-openETCS}

\input{WP41-V02-UserStory-SAAM.tex}

\subsection{Architecture Tradeoff Analysis Method (ATAM)}	
\label{sec:atam-openETCS}

\input{WP41-V02-UserStory-ATAM.tex}

\subsection{Formal Verification at Software Level}
\label{sec:form-verif-soft-openETCS}

\input{WP41-V02-UserStory-CEA-FOKUS.tex}

\subsection{Formal Model Verification (TWT)}
\label{sec:real-time-TA-openETCS}

\input{WP41-V02-UserStory-TWT.tex}


\subsection{Verification with Model-Based Simulation using SystemC (TWT, URO)}
\label{sec:model-based-sim-openETCS}
\input{WP41-V02-UserStory-TWT-URO.tex}


\subsection{System Integration  Testing (Uni Bremen/DLR)}
\input{WP41-V02-UserStory-UB.tex}


\subsection{Model Verification by applying the openETCS
  Verification Tool Chain (Siemens)}
\input{WP41-V02-UserStory-Siemens.tex}


\section{Verification Activities---Timeline}
\label{sec:verif-activ-timel}

This section lists per partner/activity in which of the project
phases according to Sec.~\ref{sec:verif-activ-timel} (first, second or
third level of verification) a particular activity is planned. In the
first version of the V\&V plan, only the first level needs to be detailed.


\subsection{First Level of Verification}
\label{sec:first-level-verif}

This section gives only a short description, which should refer to an
activity detailed earlier. Most probably the material will be
organised in a table.

\paragraph{TWT}
TWT will continue with the analysis of methods for generating SystemC
code from SysML models. In first investigations the Acceleo tool
(Eclipse plugin, based on OMG standard) seems to be a promising
candidate for model-to-text transformation. The approach will be
aligned with URO and their SystemC model of the braking curves.  See
also Sct.~\ref{sec:model-based-sim-openETCS}.

In addition, TWT will start with the analysis on whether/how UML/SysML
statecharts can be transformed to timed automata in a sensible manner
while retaining as much structural information as possible. Timed
automata provide a means for model checking real-time properties of
systems. See also Sct.~\ref{sec:real-time-TA-openETCS}.

\paragraph{URO}
URO will continue their work on a modular and executable SystemC model
for braking curves suitable for real-time simulation. An accompanying
high-level SysML model will be constructed as well and aligned with
TWT's activities on SysML $\rightarrow$ SystemC code generation.  See
also Sct.~\ref{sec:model-based-sim-openETCS}.

\paragraph{Uni. Bremen}
Uni Bremen will start by developing and setting a simulation
environment for the test of the EVC. The test models from the
model-evaluation will be completed and the breaking curves will be
added.  The set of tests generated will be then compared to the
available ones of SUBSET-076.


\subsection{Second Level of Verification}
\label{sec:secon-level-verif}

\subsection{Third Level of Verification}
\label{sec:third-level-verif}


\section{Verification Activities---Process View}
\label{sec:verif-activ-proce}
This section provides the detailed plan for the verification tasks
throughout the openETCS project life cycle. It summarizes the
activities performed by the project partners in relating them to the
overall definition of verification activities in
Sec.~\ref{sec:verif-full-devel}. 

\section{Verification Reporting}
This section describes how the results of implementing the
Verification Plan will be documented.  Verification reporting will
occur throughout the software life cycle.  The content, format, and
timing of all verification reports shall be specified in this section.

\bgcmmnt{Here we need the template for reporting.}

\nthng{\textit{This subsection has to be revised to fit the restrictions of implementability within the project.}}

The following reports will be generated during the verification process:
\begin{itemize}
\item \textbf{Anomaly reports:} 
\item \textbf{Phase Summary Verification reports:} 
\item \textbf{Final report:}
\end{itemize}

The structure of the Verification report is already defined in the
\ref{sec:struct-verif-report} section of this document 

\section{Administrative procedures}
This section identifies the existing administrative procedures that
are to be implemented as part of the Verification Plan. 
Verification efforts consist of both management and technical tasks.
Furthermore, it is the task of the SQA team to monitor whether the
procedures as defined in the management plans ([QAplan], [SCMP],
[Review and Revision processes]) are followed. 

\subsection{Problem Report}
The problem reporting procedure is described within the document
Change/Problem Management Process.

Any problem, failure and error encountered during the review
activities (QA. Verification, Validation, Assessment) planned in the
software development life-cycle, problems reported by users and
customers as well as change requests initiated by any of the system
stakeholders will be reported and managed following the Change/Problem
Management Process detailed in
\href{https://github.com/openETCS/governance/tree/master/Change-Problem%20Process}{[governance]} and through the Change/Problem Management Tool.

\subsection{Task Iteration Process}
Any change in the requirements (system, sub-systems, sw or components)
require repeated verification and validation activities. 

Once the change is accepted following the change/problem management
procedure, the phases and items affected by it must be
evaluated. These tests will be redesigned to reflect the change in the
requirement and will be executed again. 

In turn, a new analysis of the Software Integrity Level will involve
the analysis of the activities requirements and documentation
presented by the EN50128 standard and include such activities in the
SVVP if necessary. 

\subsection{Deviation Process}
The Quality Manager will be informed in the case of detection of a
deviation regarding Verification Plan. In addition, he/she also be
informed if it is deemed necessary by an amendment to the Plan,
whether or not motivated by a deviation 

The Quality Manager will report such incidents to the Project Managers
and with whom shall act appropriately. All persons listed in the
Responsibilities section (Sec.~\ref{sec:vv-responsibilities}) shall be
informed of a change in the Verification Plan

\subsection{Control Procedure}
Control procedures are specified in the Configuration Management Plan [SCMP]
