% \chapter{Validation Plan for the Project openETCS}
% \label{sec:valid-plan-open}

\section{Validation Overview}
\label{sec:valid-overv}
This section describes the validation activities which are
  planned to be performed within the project.

The timeline of validation activities parallels that of the
verfication. I.e., there are the same three levels as in
Sec.~\ref{sec:verif-overv}. 


\section{Validation Activities---User Sories}
\label{sec:valid-activ-user}

Like Sec.~\ref{sec:verif-activ-user}, this section describes the
validation activities to be performed within the project. It shall
tell coherently the \textbf{content} (method, tool, result quality) of
validation activities. Later (sub)sections provide the organisational
detail: \textbf{When} (Timeline, Sec.~\ref{sec:valid-activ-timel}) and
\textbf{Contribution} (which of the validation obligations from
Sec.~\ref{sec:valid-full-devel} are tackled by what approach.


\section{Validation Activities---Timeline}
\label{sec:valid-activ-timel}

This section lists per partner/activity in which of the project
phases according to Sec.~\ref{sec:valid-activ-timel} (first, second or
third level of validation) a particular activity is planned. In the
first version of the V\&V plan, only the first level needs to be detailed.


\subsection{First Level of Validation}
\label{sec:first-level-valid}

A short description which may refer to an activity detailed
earlier. Most probably the material will be organised in a table.

\subsection{Second Level of Validation}
\label{sec:secon-level-valid}

\subsection{Third Level of Validation}
\label{sec:third-level-valid}


\section{Validation Activities---Process View}
\label{sec:valid-activ-proce}
This section provides the detailed plan for the validation tasks
throughout the openETCS project life cycle. It summarizes the
activities performed by the project partners in relating them to the
overall definition of validation activities in
Sec.~\ref{sec:valid-full-devel}. 

